Software Ticket Quality

### 2017-10-28 proposal/mprop.tex
Add measuring data quality paper in bib
Add metrics for measuring data quality paper

>>>>

\textbf{Metrics for Measuring Data Quality}\cite{Heinrich2007MetricsDataQuality}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors of the paper aimed to answer the two main research questions:
      \begin{itemize}
        \item how can data quality be measured as metrics?
        \item what can be done in regards to data quality and what economic
          consequences would it bring?
      \end{itemize}
  \item \textbf{What was the method?}
    They applied the metric for timeliness at a major German mobile services
    provider. Due to some Data Quality issues the company was having, they had
    lower mailing campaign success rates, but after applying the metrics, the 
    company was able to establish a direct connection between the results of
    measuring data quality and the success rates of campaigns.
  \item \textbf{What did they learn?}
    For some practical problems, the metrics that they applied in regards to
    data quality proved to be quite appropriate. As they designed the metrics
    to revolve around interpretability and cardinality, they could quantify
    data quality, thus they could analyse the economical impact.
  \item \textbf{Relevance to our work}: this paper could possibly help us in
    measuring data quality. This is an important step in our research as we 
    specifically need to measure quality in software tickets.
\end{itemize}
